### 2015-01-21 paper_30_measure.tex
some section changes in chapter 3

A metric can be defined as the science of indirect measurement.
    The following are some examples of metrics that can be collected 
    about source code:
    \begin{itemize}
        \item SLOC - The number of Source Lines of Code 
        \item NOM - The Number of Methods per class
        \item Complexity - A numerical measure of the code complexity,
            some common examples are McCabe \cite{McCabe1976} and 
            Halstead \cite{Halstead1977}
        \item Design - The amount of coupling and cohesion present 
        in the software code
        \item Source Code Analysis - Tools that determine whether 
        code adheres to specified set of rules. Common 
        examples are PMD and findbugs \cite{PMD, Findbugs}.
    \end{itemize}

@@

Performance indicators can be crucial measurements
within any business setting, and an SDO is no exception. Many
SDOs struggle to determine the correct indicators to track and
how to track them.  
The differences between the indicators will be explored and
possible measures for each indicator in an SDO will be
presented.  The 4 different types of indicators are:
\begin{description}
  \item[RI (Result Indicator)] - what has been done
  \item[KRI (Key Result Indicator)] - how you have done
  \item[PI (Performance Indicator)] - what to do
  \item[KPI (Key Performance Indicator)] - what to do to dramatically increase performance
\end{description}

@@

\subsection{RESULT INDICATORS FOR SDO}
    This section will cover the potential result indicators for an SDO.

\subsection{KEY RESULT INDICATORS FOR SDO}

\subsection{PERFORMANCE INDICATORS FOR SDO}
    This section will cover the potential performance indicators for an SDO.

\subsection{KEY PERFORMANCE INDICATORS FOR SDO}

@@

A common technique for organization to measure themselves is a balanced scorecard.
A \textit{balanced scorecard} must contain the following
characteristics.
\begin{itemize}
  \item Financial 
  \item Customer Focus
  \item Environment/Community
  \item Internal Process
  \item Employee Satisfaction
  \item Learning and Growth
\end{itemize}

@@

According to Putnam and Myers in \cite{Putnam2013}, the 5 core measurements for managing software
projects are:

>>>>

A metric can be defined as the science of indirect measurement.
    The following are some examples of metrics that can be collected 
    about source code:
    \begin{itemize}
        \item SLOC - The number of Source Lines of Code 
        \item NOM - The Number of Methods per class
        \item Complexity - A numerical measure of the code complexity,
            some common examples are McCabe \cite{McCabe1976} and 
            Halstead \cite{Halstead1977}
        \item Design - The amount of coupling and cohesion present 
        in the software code
        \item Source Code Analysis - Tools that determine whether 
        code adheres to specified set of rules. Common 
        examples are PMD and FindBugs$^{TM}$ \cite{PMD, Findbugs}.
    \end{itemize}

@@

\subsection{INDICATORS}
Performance indicators can be crucial measurements
within any business setting, and an SDO is no exception. Many
SDOs struggle to determine the correct indicators to track and
how to track them.  
The differences between the indicators will be explored and
possible measures for each indicator in an SDO will be
presented.  The 4 different types of indicators are:
\begin{description}
  \item[RI (Result Indicator)] - what has been done
  \item[KRI (Key Result Indicator)] - how you have done
  \item[PI (Performance Indicator)] - what to do
  \item[KPI (Key Performance Indicator)] - what to do to dramatically increase performance
\end{description}

@@

\subsubsection{RESULT INDICATORS FOR SDO}
    This section will cover the potential result indicators for an SDO.

\subsubsection{KEY RESULT INDICATORS FOR SDO}

\subsubsection{PERFORMANCE INDICATORS FOR SDO}
    This section will cover the potential performance indicators for an SDO.

\subsubsection{KEY PERFORMANCE INDICATORS FOR SDO}

@@

A common technique for organization to measure themselves is a balanced scorecard.
A \textit{balanced scorecard} must contain the following six
characteristics.
\begin{enumerate}
  \item Financial 
  \item Customer Focus
  \item Environment/Community
  \item Internal Process
  \item Employee Satisfaction
  \item Learning and Growth
\end{enumerate}

@@

\subsection{PROJECT MANAGEMENT MEASUREMENT}
According to Putnam and Myers in \cite{Putnam2013}, the 5 core measurements for managing software
projects are:
